18S algae ASV clustering

### 2020-01-12 manuscript/supp/code/18s_asv_clust.Rmd
tweak figures

```{r, include=F}
aligns <- readDNAStringSet(here::here("data/asv_seq_data/algae_18s_quality_aligns.fasta"))
# taxonomy w genbank (multiple copies of each designation, no editing)
taxonomy <- read_csv(here::here("output/algae_18s_assignments_snow_algae_genbank.csv"))
tree <- ape::read.tree(here::here("output/tree/algae_18s/algae_18s_seqs.fasta.treefile"))
rel_abund <- read_csv(here::here("data/03_filtered/18s_algae/18s_algae.filtered_cleaned_rel_abund.csv"))

@@

>>>>

```{r, include=F}
aligns <- readDNAStringSet(here::here("data/fastas/asv_seq_data/algae_18s_quality_aligns.fasta"))
# taxonomy w genbank (multiple copies of each designation, no editing)
taxonomy <- read_csv(here::here("data/taxonomy/algae_18s_assignments_snow_algae_genbank.csv"))
tree <- ape::read.tree(here::here("data/tree/algae_18s/algae_18s_seqs.fasta.treefile"))
rel_abund <- read_csv(here::here("data/rel_abund/3_filter/18s_algae/18s_algae_rel_abund.csv"))

@@

Perplexity = 20.
